# openEO Hackathon - Solution R client / GeoPyspark back-end

## Task 1

Installing and loading the required packages:
```{r}
install.packages("devtools")
require("devtools")

# Sometimes the devtools fail to install some dependencies.
# You may need to install Rcpp and rlang manually by uncommenting thw following two lines:
# install.packages("Rcpp")
# install.packages("rlang")

install_github(repo="Open-EO/openeo-r-client",ref="develop",dependencies=TRUE)
require("openeo")
```

Connecting to the openEO Earth Engine back-end. You may need to change the credentials:
```{r}
gps.url = "http://giv-project8.uni-muenster.de"
gps.pwd = "test123"
gps.user = "groupX"
con = connect(gps.url,user=gps.user,password=gps.pwd)
```

Requesting the capabilities that are provided by the back-end:
```{r}
con %>% listCapabilities()
```

## Task 2

Requesting the processes offered by the back-end:
```{r}
con %>% listProcesses()
```

Requesting the arguments required for the ndvi process:
```{r}
con %>% describeProcess("NDVI")
```

Requesting the products offered by the back-end:
```{r}
con %>% listCollections()
```
